Viscous Transport in Eroding Porous Media

### 2019-05-31 docs/transport/erosion_transport.tex
do the result section in transport paper

Since we use a Barycentric quadrature rule to approximate the velocity of tracers
and apply the fourth order Runge Kutta method to find the new locations of tracers in each step,
the tracers can be very close to but not penetrate the bodies. 
Those body-closed tracers are moving perfectly 
so we are able to observe the details of the interaction of bodies and fluid.
Although the direction of flow is from left to right, 
the tracers will not only travel horizontally but also vertically. 
In the last three frames of Fig.~\ref{fig:Eroding20tracer}, 
some tracers climb up from right to left around the body. 
There are zoom windows of the climbing tracers trajectories 
in Fig.~\ref{fig:Eroding20zoom} and they are taken from the 
last three frames of Fig.~\ref{fig:Eroding20tracer} with more tracers. 
In Fig.~\ref{fig:Eroding20zoom} the tracers around 
the center body first go from the channel below the body, 
climb up to the left, then go to the right and join another tracers 
in the channel above the body. 
 }

@@

@@

\caption{The tortuosity of the 20 nearly touching bodies}
\end{center}
\end{figure}

>>>>

Since we use a Barycentric quadrature rule to approximate the velocity of tracers
and apply the fourth order Runge Kutta method to find the new locations of tracers in each step,
the tracers can be very close to but not penetrate the bodies. 
Those body-closed tracers are moving perfectly 
so we are able to observe the details of the interaction of bodies and fluid.
Although the direction of flow is from left to right, 
the tracers will not only travel horizontally but also vertically. 
In the last three frames of Fig.~\ref{fig:Eroding20tracer}, 
some tracers climb up from right to left around the body. 
There are zoom windows of the climbing tracers trajectories 
in Fig.~\ref{fig:Eroding20zoom} and they are taken from the 
last three frames of Fig.~\ref{fig:Eroding20tracer} with more tracers. 
In Fig.~\ref{fig:Eroding20zoom} the tracers around 
the center body first go from the channel below the body, 
climb up to the left, then go to the right and join another tracers 
in the channel above the body.

In Fig.~\ref{fig:Eroding20area} we measure the area occupied by bodies and the flow rate $U$ quantifily during the eroding. At the beggining, 62.32\% of area of $[-1,1] \times [-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing

The flow rate increases exponentially with growth rate close to $\ln10^4$. 
 }

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.45 \textwidth]{./figs/porosity20dense}
\includegraphics[width = 0.45 \textwidth]{./figs/flow_rate20dense}
\caption{\label{fig:Eroding20area}  The area fraction of 20 nearly touching eroding bodies and the incoming flow rate of U verse time.}
\end{center}
\end{figure}

@@

\caption{\label{fig:Eroding20tort} The tortuosity of the 20 nearly touching bodies}
\end{center}
\end{figure}
